Distribution-oblivious Programming with Dish

### 2019-11-21 pldi/draft.tex
Add notes in related work} git push

@@

@@

\heading{DSLs for Distribution}
At the other end of the spectrum, distributed computing frameworks~\cite{mapreduce:08, ciel:11, spark:12, naiad:13, jetstream:14} and domain-specific languages~\cite{alvaro2011consistency, distal:13, meiklejohn2015lasp, psync:16, dartagnan:18}
simplify certain patterns, 
but do not offer the flexibility of a full-fledged environment.
% suffer from a similar lack of generality by making strong assumptions about the nature of the computation---for example, strongly-eventual commutative components that can proceed in parallel.
Developing under these frameworks differs quite significantly from the development of normal (non-distributed) programs.

>>>>

\kk{Rename this section to panner activators}

@@

\kk{On our dataflow graph model: Our data flow graph model is
  different than most distributed batch and stream processing systems,
  since the shell is a hybrid between the two. Batch processing
  systems have no notion of data order, and stream processing systems
  usually have order, but none of these systems supports this notion
  of reading from different sources in sequence. Our dataflow graph
  model supports this by including information about incoming edge
  order. Another benefit of our dataflow model, is that together with
  the equations that hold on stateless and pure commands, data
  parallelism is exposed in the graph as task parallelism. This allows
  the unoptimized and optimized dataflow graph to have the same
  unified representation, and doesn't lead to an ad-hoc optimization
  of the dataflow graph as done in the other systems (the last bit is
  too aggressive). }

@@

\heading{DSLs for Distribution}
At the other end of the spectrum, distributed computing frameworks~\cite{mapreduce:08, ciel:11, spark:12, naiad:13, jetstream:14} \kk{JetStream has a very different focus} and domain-specific languages~\cite{alvaro2011consistency, distal:13, meiklejohn2015lasp, psync:16, dartagnan:18}
simplify certain patterns, 
but do not offer the flexibility of a full-fledged environment.
% suffer from a similar lack of generality by making strong assumptions about the nature of the computation---for example, strongly-eventual commutative components that can proceed in parallel.
Developing under these frameworks differs quite significantly from the development of normal (non-distributed) programs.
